\normalfont\normalsize
\chapter{Introduction}

Technology has been present in our lives for a long time and we have become so acustomed to it that we do not even realize when we are using it.

This tehnological advance has lead to inventing small devices with low power consumption and communication capabilities. They form a wireless sensor network and can be used to collect data from the environment and send them to a gateway for further processing. In a way, even the new gadgets that have appeared this year, gadgets like smartwatches and fitness trackers, can be seen as wireless sensor devices because they collect data like stepts, heart rate and have wireless capabilities.

The applications of a wireless sensor network are unlimited in number. For example they can be used to monitor crops, to detect possible forest fires, to detect the presence of animals or vehicles in certain areas, tracking and monitoring doctors in hospitals, guidance interactive toys, detecting and monitoring car thefts etc. In the last ten years, integration of wireless sensor networks with unmaned aerial vehicles had been tested and proven to be succesful. So far, the proposed implementations , described in chapter \ref{chap:related}, are complicated, difficult to operate and too expensive for the general public.

The solution that we propose is based on a verypopular, easy to use AR Parrot Drone 2.0 and the Sparrow Family \cite{voinescu2013lightweight}, developed at Polytehnic University of Bucharest by Andrei Voinescu.
