\normalfont\normalsize
\chapter{Future Work}

Even though the solution is working, new application and functionalities can be added. The application can be from opposing worlds, such as search and rescue versus military.


\section{Features}

\subsection{Debug}

A feature that can be used in conventional wireless sensor networks is to determine the source of communication failure. If the gateway detects that the network has a communication problem and not all of the previous nodes can be reached, this information will be send to the drone and it will try to find and determine which nodes are working properly and which nodes are not.

\subsection{Truly Autonomous flight}
The AR Parrot Drone 2.0 can perform autonomous flight with a GPS module, but only while it is still in the range of the WiFi connection.

\section{Applications}

\subsection{Treasure Hunt Games}
A treasure hunt game can be played by placing the nodes with information regarding the location of the treasure at certain hidden spots and trying to find the treasure by following the clues provided by the drone.

\subsection{Search and Rescue}
%? Nu sunt de acord că merge. Dacă știu coordonatele, dau telefon cu ele și gata. De asemenea, cu 70m în câmp deschis nu faci nimic pe munte.

%% nu s-ar putea folosi pentru ski ?  cand mergi la ski porti un sezor si duci drona rapid sa vezi daca e cineva prins si in caz de alta avalansa pierzi alta drona, nu om

When tourists go hiking or other similar activities and get lost they can be found if they are wearing a wireless sensor that monitor vitals and can gather a periodical GPS position. The drone will search for the signal emitted by the node and help pinpointing their exact location while offering a live video feed of them.

\clearpage
