Security is of prime importance in Wireless Sensor Networks. Nodes transfer important data between
them and the cost of checking the validity and integrity of the transmitted packages is high, both from 
the energy consumption perspective as well as the necessary computational power perspective.

Possible attacks that might hinder the activity and integrity of a Wireless Sensor Network include:
\begin{itemize}

\item Wormhole attack: the attacker sends the received messages from one part of the network in a different part of the network. As a result, the nodes from both areas consider that the other nodes are neighbours and vice-versa.
\item Blackhole/Sinkhole attack: the attackers makes itself more appealing from a routing point of view in order to receive all the messages from the network.
\item Sybil attack: the attacker assumes the identity of one or more valid sensors\cite{newsome2004sybil}.
\item Selective forwarding attack: the attacker is able to intercept messages and drop certain packets or forward them \cite{kaplantzis2007detecting}.
\item Hello Flood Attack: the attacker uses "HELLO" packets to flood its neighbors in order to force the nodes to trust him.

\end{itemize}

No current security framework available for Wireless Sensor Networks offers complete protection
against all types of attacks. However they offer protection against specific attacks. All of the following implementations rely on 
software encryption methods:
\begin{itemize}

\item SPINS - 2002 - The communication parties create independent keys for encryption and decryption
and MAC keys for communication. It provides security against Data and Information Spoofing and Message Replay Attacks\cite{perrig2002spins}.

\item LEAP - 2003 - The protocol implies that the nodes exchange more than one type of message between them.Thus, the framework uses 4 different keys. It provides security against "HELLO" flood attacks, Sybil attacks and minimizes the consequences of spoofing, altering, replay routing information and selective forwarding attacks \cite{zhu2006leap+}.

\item TinySec - 2004 - The key is pre-deployed on the node, but it does not provide any solution for changing the key. If a node is compromised, the entire network will be compromised. It provides security against Data and Information Spoofing and Message Replay Attacks \cite{karlof2004tinysec}.

\item LEAP+ - 2006 - It uses the same idea as LEAP, but the overhead is reduced. It provides security against Confidentiality and authentication, "HELLO" flood attacks, Sybil attacks and minimizes the consequences of spoofing, altering, replay routing information and selective forwarding attacks \cite{zhu2006leap+}.
 
\item MiniSec - 2007 - Uses a counter IV mechanism. The counter is incremented locally and only the last bits of the counter are sent. It provides security against Authentication, Data Secrecy and Reply Attack \cite{luk2007minisec}.

\item pDCS - 2009 - It uses 5 different keys to achieve data security. It provides security against Location and Query privacy \cite{shao2009pdcs}.

\item TinyKey - 2011 - An improvement of TinySec. It adds the key management system, in order to be able to change the key after the node is deployed. It provides security against Message authentication, confidentiality and integrity \cite{doriguzzi2011tinykey}.

\item ERP-DCS - 2013 - It proposes a different way of creating and storing keys when compared with pDCS. It provides security against Location and Query privacy \cite{huang2013efficient}.

\end{itemize}
