% ********** Abstract **********
\chapter*{Abstract}

This thesis proposes a new way of implementing a mobile gateway for Wireless Sensor Networks that simplifies applications running in remote locations, where maintenance is difficult. Wireless Sensor Networks islands need a gateway connection in order to reach the outside world, but this is difficult to provide in all instances.  The solution to this problem is to use a gateway mounted on a UAV that can reach those islands and extract data from them. This has been proven to be feasible but adoption is low because of the high cost and the technical background needed to operate it. We propose a simpler, easier to operate and cheaper solution for this problem.


 

\textbf{Keywords} Wireless Sensor Networks, drones, sparrow, mobile, gateway, aerial

\chapter*{Acknowledgements}

Foremost, I would like to express my gratitude to my advisor As. Drd. Ing. Andrei Voinescu for the continuous support support of my thesis.

Besides my advisor, I would also like to give special thanks to Dan Dragomir for helping me correct this work and for believing in me that I could finish this thesis. 
  
My sincere thanks also goes to Adriana Drăghici, Alexandru Corneliu Olteanu and Dan Ștefan Tudose for their insightful comments  and moral support.

I thank my fellow labmates in Robolab robotics group: Tudor Vișan, Andrei Mușat and Andrei Vasiliu for the sleepless nights we were working together before deadlines, and for all the fun we have had in the last four years.

Last but not the least, I would like to thank my family who have shown understanding and have given me the moral support needed.

% ********** End of Abstract **********
