\chapter{Conclusions}


The Wireless Sensor Networks are expanding more and more because they make our lives simpler by giving us information about our surroundings. But the standard way of creating wireless sensor network islands is not always feasible.

The main purpose of this thesis was to bring an alternative at how the data is obtained from the Wireless Sensor Network islands. We have proven that the modified drone offers a good range, being able to communicate with the nodes from a big distance. The communication range is greatly affected by the power of the antenna and the objects that obturate the line of sight from the drone to the node.


The solution, a truly mobile gateway is a viable one and it can be implemented with a relatively low cost and the necessary technical knowledge to operate the system is none other than knowing how to use a smartphone.


%Besides the practicality aspect of the solution, it can be used as a fun instrument too. A treasure hunt game can be played by placing the nodes with information regarding the location of the treasure at certain hidden spots and trying to find the treasure by following the clues provided by the drone. Other fun games that can be played is hiding the nodes in a certain zone. The players must find as many nodes as possible in that zone before the drone runs out of battery. The winner will be the player that found the largest number of nodes and has the best time.


\section{Outlook}

The solution is not in its final state and can be improved by adding new features. A feature that can be used in conventional wireless sensor networks is to determine the source of communication failure. If the gateway detects that the network has a communication problem and not all of the previous nodes can be reached, this information will be sent to the drone and it will try to find and determine which nodes are working properly and which nodes are not.

The AR Parrot Drone 2.0 can perform autonomous flight with a GPS module, but only while it is still in the range of the Wi-Fi connection. This feature will allow the drone to fly without the need to still be connected through Wi-Fi to a controlling device. Also, a different autonomous flight can be performed without a GPS module if the signal strength of the nodes is used to performed flight correction and determine the speed and direction of the drone.

